\documentclass[letter]{letter}

\usepackage{lmodern}
\usepackage[english]{babel}

\makeatletter
\let\@texttop\relax
\makeatother

\signature{\hfill Ryan Wilcox}
\address{Ryan Wilcox \\ 7187 Santa Cruz Circle \\ Buena Park, CA 90620 \\ (714) 699-1526 \\ ryanbrodrick@gmail.com}
\telephone{(714) 699-1536}

\usepackage{geometry}
%\usepackage[top=1in,bottom=1in]{geometry}
\begin{document}
\begin{letter}{JPL \\ 4800 Oak Grove Road \\ La Ca\~nada Flintridge, CA 91011}
\opening{Dear Sir or Madam:}
  
I have had a life long admiration for NASA, and --- in particular ---
the importance of the work done at JPL.  I recognize the fierce
competition for open internships with JPL, and I realize that I, like
all human beings, have a vast potential for further improvement; and
thus, I know that I could benefit from the experience of entering into
the JPLUS program.

Having attended many JPL Open Houses, I am excited about the possibility
of entering the JPLUS program.  As a child I often dreamed of someday
working at JPL, and the JPLUS program will help in realizing that
childhood dream.  Indeed, as a child I often enjoyed talking to the JPL
researchers about physics, in particular I really liked asking them
about many topics, including how gravity works on a theoretical level.
In addition, I also loved seeing the facilities at JPL, including the
machining, integrated circuit fabrication, and apparatus testing labs
containing such impressive instruments as the ion propulsion engines,
and the micro-thrusters used for positioning satellites.

As a student in Computer Science with a life long commitment to
learning, I believe that I would be a good fit for the JPLUS program.
In addition, I have a cumulative GPA of 3.8 out of 4.0 for 30 units of
college credit with 4 more units on the way.  I also have the ---
perhaps rather unreasonable --- hope of transferring to Stanford
University.  However, due to the unlikelihood of getting into Stanford
University, I will also be applying to UC Irvine and several other
research universities.  My chosen career is software engineering, and I
would like to work in a research setting.

\closing{\hfill Sincerely,}
\encl{Resume}
\encl{Transcripts: Copper Mountain College}
\encl{Transcripts: Cypress College}
\encl{Application form}
\end{letter}
\end{document}