\documentclass{res}
\newsectionwidth{0pt}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{24pt}
\setlength{\headsep}{24pt}
\pagestyle{fancy}
\rhead{ {\it R. Wilcox}\\ {\it p. \thepage} }
\cfoot{}
\usepackage[top=0.5in, bottom=0.4in]{geometry}

\begin{document}
\thispagestyle{empty}
\name{RYAN WILCOX \\ ryanbrodrick@gmail.com \\[12pt]}

\address{{\bf School Address} \\ Cypress College \\ 9200 Valley View
Street \\ Cypress, CA 90630 \\ (714) 484-7000}

\address{{\bf Permanent Address} \\ 7187 Santa Cruz Circle \\ Buena
Park, CA 90620 \\ (714) 699-1536 }

\begin{resume}

\section{\centerline{SUMMARY}}
As a college student majoring in computer science, and a self described
autodidact, who has a love for science and technology and a strong
passion for learning, I have spent a large amount of time in and outside
of classes studying a wide variety of subjects, including physics,
computer science, programming, mathematics, electronics, and foreign
language.

\section{\centerline{EDUCATION}}
{\sl Student}, Computer Science
\hfill January 2014 -- present
\\ Cypress College, Cypress, CA

{\sl Student}, Computer Science
\hfill January 2012 -- May 2013
\\ Copper Mountain College, Joshua Tree, CA
\\ Cumulative GPA of 3.8
\\ Honer roll for 3 semesters with GPA of 4.0

{\sl General Education}, Homeschooled, Equivalent of High school
\hfill July 2012
\\ Desert Academy of Arts and Sciences, Yucca Valley, CA

\section{\centerline{EXPERIENCE}}
Worked with microcontroller programming. \hfill 2009--present \\
Learned to use cross-compilers and upload code to microcontrollers. \\
Debugged microcontrollers via serial input. \\
Primarily experimented with the following:
\begin{itemize}
 \item Standard blinking lights and button press detection setups.
 \item Reading analog signals via DACs.
 \item Attempted detection of electromagnetic fields via floating analog
       input.
\end{itemize}

Developed physics simulations and control systems demonstration
programs.  \hfill 2008

Worked on and off in my family's construction business. \hfill
2005--present

At an age of 7, learned scripting in a game to make custom
content. \hfill 2000

\section{\centerline{SKILLS}}
\begin{itemize}
 \item Comfortable with programming in C++ --- 2009 \& 2014
 \item Familiar with Lua, R, Maxima, and Postscript programming ---
       2012--2014
 \item Knows, and has written several programs in, RPL for the HP50g
       graphing calculator --- 2013
 \item Has written several programs in and is quite comfortable with
       programming in Common LISP --- 2011--present
 \item Able to understand and work with programs written in Scheme,
       Perl, and JavaScript --- 2011--present
 \item Knows BASH scripting, used on daily basis --- 2008--present
 \item Makes extensive use of Linux as primary OS since 2008
 \item Able to work with Pascal source code --- 2007
 \item Written several programs in Python --- 2006--present
 \item Basic understanding of electrical engineering and design ---
       2002--present
\end{itemize}

\end{resume}

\end{document}
