\documentclass{res} 
%\usepackage{helvetica}
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it R. Wilcox}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
%\topmargin=-0.5in % start text higher on the page
\usepackage[top=0.5in, bottom=0.5in]{geometry}

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{RYAN WILCOX\\[12pt]}% the \\[12pt] adds a blank line after name

\address{{\bf School Address} \\ Copper Mountain College \\ 6162 Rotary
  Way \\ Joshua Tree, CA 92252 \\ (760) 366-3791}
                                      
\address{{\bf Permanent Address} \\ 57855 Desert Gold Drive \\ Yucca
  Valley, CA 92284 \\ (760) 365-0743 }



\begin{resume}
 
\section{\centerline{OBJECTIVE}}
\vspace{8pt} % provide vertical space between section title and contents
Intern for general programming and/or software development.

\section{\centerline{EDUCATION}} 
\vspace{8pt} 
{\sl Student}, Computer Science \\ Copper Mountain College, Joshua Tree,
CA \hspace{0.1in} % Would put GPA here.
\hfill December 2012 \\

{\sl General Education}, Homeschooled, Equivalent of High school \\
Desert Academy of Art and Science, CA \hfill July 2012

\section{\centerline{PROFESSIONAL EXPERIENCE}} 
\vspace{8pt}

{\sl Personal Projects} \hfill April 1993 - Present
 \begin{itemize}
  \item Personal website (\texttt{http://ryanbw.sdf.org/}) A personal
        website developed from scratch, using HTML, CSS, and a
        home-built Python CGI script based template system.
  \item A Python based RTS game engine, rendering system only.
 \end{itemize}

{\sl The Glass Fixer} \hfill January 2012 - Present \\ Part-time
Technical Consultant, Yucca Valley, CA
 \begin{itemize}
  \item Provided general IT advice, QA, and guidance.
 \end{itemize}

{\sl A Design For Living} \\[2pt] Part-time Technical Consultant, Yucca
Valley, CA \hfill 2010 - 2012
 \begin{itemize}
  \item Provided general IT advice, QA, and guidance.
 \end{itemize}

{\sl Wilcox Construction} \\ Part-time Web Developer and Technology
Consultant, Yucca Valley, CA \hfill 2011 - 2012
 \begin{itemize}
  \item Created the initial website they used their first month of
        business, used a combination of HTML, CSS, and JavaScript to
        create smooth website with a slide show.
  \item Provided technical consultation on various IT matters.
 \end{itemize}


\section{\centerline{PROFICIENT WITH THE FOLLOWING TECHNOLOGIES}} 
\vspace{8pt}
Over 5 years with various Linux distributions, including Ubuntu, Debian,
and Gentoo.

Competent in the following languages, Python, Common LISP, Emacs LISP,
and BASH.  Familiar with the following, C, C++, Java, JavaScript, Perl,
and Pascal.

Very experienced with the Emacs text editor and IDE.  Very comfortable
with the command-line.


\section{\centerline{HONORS}} 
\vspace{-5pt}
\begin{center}
Honer Roll, Spring Semester, 2012, 4.00 GPA
\end{center}
 
\section{\centerline{INTERESTS}} 
\vspace{-5pt} 
\begin{center}
Classical music, playing various instruments, retro technology,
electronics, amateur radio, writing, and advanced mathematical theory.
\end{center} 


\end{resume} 
\end{document}
