\documentclass{res}
\newsectionwidth{0pt}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{24pt}
\setlength{\headsep}{24pt}
\pagestyle{fancy}
\rhead{ {\it R. Wilcox}\\ {\it p. \thepage} }
\cfoot{}
\usepackage[top=0.5in, bottom=0.4in]{geometry}

\begin{document}
\thispagestyle{empty}
\name{RYAN WILCOX \\ ryanbrodrick@gmail.com \\[12pt]}

\address{{\bf Permanent Address} \\ 7187 Santa Cruz Circle \\ Buena
Park, CA 90620 \\ (714) 699-1536 }

\begin{resume}

\section{\centerline{SUMMARY}}
As a college student majoring in computer science, and a self described
autodidact, who has a love for science and technology and a strong
passion for learning, I have spent a large amount of time in and outside
of classes studying a wide variety of subjects, including physics,
computer science, programming, mathematics, electronics, and foreign
language.

\section{\centerline{EDUCATION}}
{\sl Student}, Computer Science
\hfill January 2014 -- present
\\ Cypress College, Cypress, CA

\section{\centerline{PROJECTS}}
Worked with microcontroller programming. \hfill 2009--present \\
Learned to use cross-compilers and upload code to microcontrollers. \\
Debugged microcontrollers via serial input. \\
Primarily experimented with the following:
\begin{itemize}
 \item Standard blinking lights and button press detection setups.
 \item Reading analog signals via DACs.
 \item Attempted detection of electromagnetic fields via floating analog
       input.
\end{itemize}

Developed physics simulations and control systems demonstration
programs.  \hfill 2008

%\section{\centerline{SKILLS}}
\begin{itemize}
 \item Comfortable with programming in C++ \hfill 2009 \& 2014
 \item Familiar with Lua, R, Maxima, and Postscript programming \hfill
       2012--2014
 \item Knows, and has written several programs in, RPL for the HP50g
       graphing calculator \hfill 2013
 \item Has written several programs in and is quite comfortable with
       programming in Common LISP \hfill 2011--present
 \item Able to understand and work with programs written in Scheme,
       Perl, and JavaScript \hfill 2011--present
 \item Knows BASH scripting, used on daily basis \hfill 2008--present
 \item Makes extensive use of Linux as primary OS since 2008
 \item Able to work with Pascal source code \hfill 2007
 \item Written several programs in Python \hfill 2006--present
 \item Basic understanding of electrical engineering and design \hfill
       2002--present
\end{itemize}

\end{resume}

\end{document}
